Transforming Trash as an Artistic Act

### 2016-01-08 main.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
Reorganization.
Former-commit-id: 1502aeed78b3566ee9739270b736389b7fc1099d
fixing errors
Former-commit-id: 9b772b65c5da763a5a43ec58ca1814033107f57e

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,left=40mm,right=25mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc]{appendix}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{afterpage}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

@@

\usepackage{natbib}
\setlength{\bibsep}{0.0pt}

@@

@@

% Chapter title spacing
\titlespacing{\chapter}{0pt}{25mm}{3\baselineskip}

% EPIGRAPH
\setlength{\epigraphwidth}{.6\textwidth}
\setlength{\epigraphrule}{0pt}

\hypersetup{
    pdftitle			= {MFA Thesis},
    pdfauthor			= {Mustafa ilhan},
    pdfsubject			= {Trash, Art},
    pdfkeywords			= {mfa thesis, trash, art},
    colorlinks			= false,
    pdfborder			= {0 0 0},
    pdfpagemode			= UseOutlines
}

\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}
\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
\providecommand{\summary}[1]{\textcolor{blue}{[#1]}}
\providecommand{\paraphrase}[1]{\textcolor{magenta}{\quotes{#1}}}

@@

%****************************************
% Title Ideas for Thesis 
% - Trash as an Artistic Medium
% - Notebooks from Trash: Trash in the Context of Art
% - Notebooks from Trash: Exploring the potential of trash through art practice
% - Transforming Trash as an Artistic Act
% - Act of Transforming Trash in the Context of Art
%........................................

@@

        \vspace*{25mm}
        \uppercase{Transforming Trash as an Artistic Act}

        \vspace{15mm}
        A Master’s Thesis\\
        \vspace{15mm}
        by\\
        MUSTAFA İLHAN

        \vfill
        Department of\\
        Communication and Design\\
        İhsan Doğramacı Bilkent University\\
        Ankara\\
        January 2016
        \vspace{25mm}

@@

        \vspace*{25mm}
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        \vspace*{4\baselineskip}
        Graduate School of Economics and Social Sciences\\
        of\\
		İhsan Doğramacı Bilkent University\\
		\vspace*{3\baselineskip}
        by\\
       	\vspace*{3\baselineskip}
        MUSTAFA İLHAN\\
        \vspace*{4\baselineskip}
        In Partial Fulfilment of the Requirements for the Degree of\\
		MASTER FINE OF ARTS\\
        \vspace{2\baselineskip}
        in\\
        \vspace{2\baselineskip}
        THE DEPARTMENT OF\\
        COMMUNICATION AND DESIGN\\
       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
        ANKARA\\
        \vspace{\baselineskip}
        January 2016
	\end{center}
\clearpage
%........................................

@@

%****************************************
% ENGLISH ABSTRACT
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\doublespacing
\begin{center}
	\vspace*{25mm}
	\MakeUppercase{Abstract}\\
    \vspace{\baselineskip}
    TRANSFORMING TRASH AS AN ARTISTIC ACT\\
    İlhan, Mustafa\\
    M.F.A., Department of Communication and Design\\
    Supervisor: Assist. Prof. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    January 2016
\end{center}
\singlespacing
\par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century. This approach has broken the existing rules and extended the language of art in an unprecedented way. After that point, trash has found a place in the work of artists.

@@

%****************************************
% TURKISH ABSTRACT
\thispagestyle{plain}
\selectlanguage{turkish}
\phantomsection
\addcontentsline{toc}{chapter}{ÖZET}
\doublespacing
\begin{center}
	\vspace*{25mm}
	\MakeUppercase{Özet}\\
    \vspace{\baselineskip}
    \MakeUppercase{Sanatsal Bir Eylem Olarak Atığı Dönüştürme}\\
    İlhan, Mustafa\\
    Yüksek Lisans, İletişim ve Tasarım Bölümü\\
    Tez Yöneticisi: Yrd. Doç. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    Ocak 2016
\end{center}
\singlespacing
\par Sanat işlerinde sanat dışı nesnenin kullanımı 20. yüzyılın başına kadar takip edilebilmektedir. Bu yaklaşım var olan kuralları yıkmış ve sanatın dilini eşi görülmemiş bir biçimde genişletmiştir. Bu noktadan sonra atık sanatçıların işlerinde yer bulmuştur.

@@

%****************************************
% ACKNOWLEDGMENTS
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\doublespacing
\begin{center}
	\vspace*{25mm}
	\MakeUppercase{ACKNOWLEDGMENTS}\\
    \vspace{3\baselineskip}
\end{center}
\par First and foremost, I would like to thank to my thesis supervisor Assist. Prof. Dr. Ersan Ocak for his endless patience, support and encouragement through the whole progress. He contributed in every way he can and guided me through the development of this thesis with his immense knowledge. I also would like to thank the rest of my thesis committee; Prof. Dr. Mehmet Yılmaz and Instructor Ekin Kılıç for their valuable contributions and insightful comments on the issues of this thesis.

@@

\setlength{\cftbeforetoctitleskip}{25mm}
\setlength{\cftaftertoctitleskip}{3\baselineskip}
\setlength{\cftchapnumwidth}{7em}
%\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}

@@

@@

\setlength{\cftbeforeloftitleskip}{25mm}
\setlength{\cftafterloftitleskip}{3\baselineskip}

\begin{singlespace}
\listoffigures
\end{singlespace}
\clearpage
%{%
%\let\oldnumberline\numberline%
%\renewcommand{\numberline}{\figurename~\oldnumberline}%
%\listoffigures%
%}
%........................................

@@

%\listoftodos

@@

@@

%****************************************
% APENDICES
\begin{appendices}
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
\include{appendix_glossary}
\include{appendix_materials}
\include{appendix_project}
\end{appendices}
%........................................

>>>>

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,left=40.1mm,top=24.1mm,right=25.1mm,bottom=36mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames,dvipsnames]{color}
\usepackage[titletoc,title]{appendix}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{afterpage}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

@@

% Bibliography line spacing
\usepackage{natbib}
\setlength{\bibsep}{0.0pt}

\usepackage{xpatch}

\xpatchbibmacro{date+extrayear}{%
  \printtext[parens]%
}{%
  \setunit*{\addperiod\space}%
  \printtext%
}{}{}

% Footnote line spacing
\setlength{\footnotesep}{\baselineskip}

@@

% Quote spacing
\expandafter\def\expandafter\quote\expandafter{\quote\singlespacing}

@@

% Chapter title spacing
\titlespacing{\chapter}{0pt}{9mm}{3\baselineskip}

% Epigraph setup
\setlength{\epigraphwidth}{.65\textwidth}
\setlength{\epigraphrule}{0pt}

% PDF setup
\hypersetup{
    pdftitle			= {MFA Thesis},
    pdfauthor			= {Mustafa ilhan},
    pdfsubject			= {Trash, Art},
    pdfkeywords			= {mfa thesis, trash, art},
    colorlinks			= false,
    pdfborder			= {0 0 0},
    pdfpagemode			= UseOutlines
}

% Utilities
\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}
\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
\providecommand{\summary}[1]{\textcolor{blue}{[#1]}}
\providecommand{\paraphrase}[1]{\textcolor{magenta}{\quotes{#1}}}

@@

@@

        \vspace*{20mm}
        \uppercase{Transforming Trash as an Artistic Act}\\
        \vspace*{3\baselineskip}
        A Master’s Thesis\\
        \vspace*{3\baselineskip}
        by\\
        MUSTAFA İLHAN

        \vfill
        Department of\\
        Communication and Design\\
        İhsan Doğramacı Bilkent University\\
        Ankara\\
        January 2016
        \vspace*{28mm}

@@

        \vspace*{25mm}
        TRANSFORMING TRASH AS AN ARTISTIC ACT\\
        \vspace*{4\baselineskip}
        Graduate School of Economics and Social Sciences\\
        of\\
		İhsan Doğramacı Bilkent University\\
		\vspace*{2\baselineskip}
        by\\
       	\vspace*{2\baselineskip}
        MUSTAFA İLHAN\\
        \vspace*{3\baselineskip}
        In Partial Fulfilment of the Requirements for the Degree of\\
		MASTER OF FINE ARTS\\
        \vspace{\baselineskip}
        in\\
        \vspace{\baselineskip}
        THE DEPARTMENT OF\\
        COMMUNICATION AND DESIGN\\
       	İHSAN DOĞRAMACI BİLKENT UNIVERSITY\\
        ANKARA\\
        \vspace{\baselineskip}
        January 2016
	\end{center}
\clearpage
%........................................

@@

%****************************************
% ENGLISH ABSTRACT
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRACT}
\doublespacing
\begin{center}
	\vspace*{7mm}
	\MakeUppercase{Abstract}\\
    \vspace{\baselineskip}
    TRANSFORMING TRASH AS AN ARTISTIC ACT\\
    İlhan, Mustafa\\
    M.F.A., Department of Communication and Design\\
    Supervisor: Assist. Prof. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    January 2016
\end{center}
\singlespacing
\par Usage of non-art objects in the artworks can be traced back to the beginning of 20th century. This approach has broken the existing rules and extended the language of art in an unprecedented way. After that point, trash has found a place in the work of artists.

@@

%****************************************
% TURKISH ABSTRACT
\thispagestyle{plain}
\selectlanguage{turkish}
\phantomsection
\addcontentsline{toc}{chapter}{ÖZET}
\doublespacing
\begin{center}
	\vspace*{9mm}
	\MakeUppercase{Özet}\\
    \vspace{\baselineskip}
    \MakeUppercase{Sanatsal Bir Eylem Olarak Atığı Dönüştürme}\\
    İlhan, Mustafa\\
    Yüksek Lisans, İletişim ve Tasarım Bölümü\\
    Tez Yöneticisi: Yrd. Doç. Dr. Ersan Ocak\\
    \vspace{\baselineskip}
    Ocak 2016
\end{center}
\singlespacing
\par Sanat işlerinde sanat dışı nesnenin kullanımı 20. yüzyılın başına kadar takip edilebilmektedir. Bu yaklaşım var olan kuralları yıkmış ve sanatın dilini eşi görülmemiş bir biçimde genişletmiştir. Bu noktadan sonra atık sanatçıların işlerinde yer bulmuştur.

@@

%****************************************
% ACKNOWLEDGMENTS
\thispagestyle{plain}
\phantomsection
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\doublespacing
\begin{center}
	\vspace*{7mm}
	\MakeUppercase{ACKNOWLEDGMENTS}\\
    \vspace{3\baselineskip}
\end{center}
\par First and foremost, I would like to thank to my thesis supervisor Assist. Prof. Dr. Ersan Ocak for his endless patience, support and encouragement through the whole progress. He contributed in every way he can and guided me through the development of this thesis with his immense knowledge. I also would like to thank the rest of my thesis committee; Prof. Dr. Mehmet Yılmaz and Instructor Ekin Kılıç for their valuable contributions and insightful comments on the issues of this thesis.

@@

\setlength{\cftbeforetoctitleskip}{19mm}
\setlength{\cftaftertoctitleskip}{3\baselineskip}
\setlength{\cftchapnumwidth}{7em}
%\addtolength{\cftchapnumwidth}{\cftchappresnum\cftchapaftersnum}

% Spacing between items
\setlength{\cftbeforesecskip}{\cftbeforechapskip}
\setlength{\cftbeforesubsecskip}{\cftbeforechapskip}

@@

% Spacing between items
\makeatletter
\def\@chapter[#1]#2{\ifnum \c@secnumdepth >\m@ne
	\refstepcounter{chapter}%
	\typeout{\@chapapp\space\thechapter.}%
	\addcontentsline{toc}{chapter}%
	{\protect\numberline{\thechapter}#1}%
	\else
	\addcontentsline{toc}{chapter}{#1}%
	\fi
	\chaptermark{#1}%
	\if@twocolumn
	\@topnewpage[\@makechapterhead{#2}]%
	\else
	\@makechapterhead{#2}%
	\@afterheading
	\fi}
\makeatother

@@

\setlength{\cftbeforeloftitleskip}{19mm}
\setlength{\cftafterloftitleskip}{3\baselineskip}
\setlength{\cftbeforefigskip}{\cftbeforechapskip}

\begin{singlespace}
\listoffigures
\end{singlespace}
\clearpage
%........................................

@@

@@

% TODO yıl olayını düzeltmeli
% Bibliographyden sonra 4 boşluk olmalı?

@@

%****************************************
% APENDICES
%\appendix

%\addtocontents{toc}{\cftpagenumbersoff{chapter}} 
%\chapter*{APPENDICES}
%\addtocontents{toc}{\protect\contentsline {chapter}{APPENDICES}{}{}}

%\addtocontents{toc}{\cftpagenumberson{chapter}}

%\makeatletter
%\addtocontents{toc}{\let\protect\l@chapter\protect\l@section}
%\makeatother

%\include{appendix_glossary}
%\include{appendix_materials}
%\include{appendix_project}
%........................................
